%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Damien} % Your first name
\familyname{C. Jacques} % Your last name
\title{Consultant in data innovation, PhD}
% All information in this block is optional, comment out any lines you don't need

%\address{B Block,Sector 62}{Noida, UP}
\mobile{+32-476685987}
\email{damienjacquesUCL@gmail.com}
\homepage{www.damienjacques.com}{www.damienjacques.com} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
 % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title


\vspace{-1mm}
\section{Summary}

Freelance consultant, expert in data innovation for development. Led projects across the globe requiring: (i) designing and implementing algorithms and apps to extract key insights from large unstructured data, (ii) develop strategies to leverage the entire data value chain of companies and development agencies; and (iii) successfully scale up data solutions in complex and multi-stakeholder ecosystem. Strong academic track record through several projects in Data Science and AI for social good (including projects in food security, poverty and agricultural economics). Awarded the Agriculture prize in the Data For Development (D4D) challenge organized by Orange, MIT, and the UN. Worked with US and Belgian universities and various international organizations engaged in development. Hold a Ph.D. in Bioengineering and Agronomy from the catholic University of Louvain.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}

\cventry{2013 - 2018}
    {Ph.D. Degree in Agronomy and Bioengineering}
    {\textsc{catholic University of Louvain}}
    {Belgium}{}
    {Dissertation:  \emph{\href{https://bit.ly/2BYyEF3}{Harnessing the Data Revolution for Food Security and Poverty Mapping: Synergies between Mobile Phone Data, Earth Observation and Official Statistics in Senegal}}. Advisors: Prof. Pierre Defourny.}
    
    
\cventry{2010 - 2012}
    {Master's Degree in Bioengineering - Environment}
    {\textsc{catholic University of Louvain}}
    {Belgium}{}
    {Dissertation: \emph{\href{http://bit.ly/1U7Bi9V}{Dry vegetation monitoring in Sahel}}.  Advisors: Prof.  Pierre Defourny, Dr. Pierre Hiernaux, Dr. Laurent Kergoat.}
    

        
\cventry{2007 - 2010}
  {Bachelor's Degree in Bioengineering - Environmental engineering}
    {\textsc{University of Liège - Gembloux Agrobiotech}}
    {Belgium}{}
    {}  
    

\section{Experience}

\cventry{2019 - 2020}{Technical Consultant}{\textsc{Rubyx}}{}{Belgium}{\textnormal{Technical support in the designing and production of decision support applications for microfinance institutions in Africa.}}

\cventry{2019 - 2020}{Technical Expert}{\textsc{Dalberg Data Insights}}{}{Belgium}{\textnormal{Multifaceted responsibility covering business development activities (client prospecting, proposal writing), project management, technical implementation (development of decision making applications and algorithms for analyzing large datasets), external communication (blog writing and promotional video production), conference organization, and strategy consulting. Actively contributed to financial inclusion, epidemiology, food security and poverty-related projects in different countries in Africa and South America involving many international partners such as GIZ, Experian, MTN, GiveDirectly, the World Bank and the Qatar Computing Research Institute.}}

\cventry{2019 - 2020}{Research Consultant}{\textsc{Inter-American Development Bank}}{}{Nicaragua}{\textnormal{Research and analysis of a unique mobile phone dataset to study the impact of the socio-economic crisis of April 2018 on poverty in Nicaragua. Preparation of a detailed report including a comprehensive literature review, the results of a predictive (machine learning) and descriptive (statistics and econometrics) analysis of poverty dynamics using relevant variables from the mobile phone data, and a list of recommendations for further research.}}

\cventry{2019}{Postdoctoral Researcher}{\textsc{University of California, Los Angeles}}{}{USA}{\textnormal{Contribution to a research project on the impact of short and long-term migration derived from census and mobile phone data on HIV prevalence in Botswana.}}

\cventry{2017 - 2018}{Research Assistant}{\textsc{Free University of Brussels}}{}{Belgium}{\textnormal{Research work on the study of the dynamics of the Belgian population using mobile phone data. Literature review, statistical analysis of the data, modelling and visualisation of the results through interactive applications.}}

\cventry{2013 - 2018}{PhD Candidate}{\textsc{catholic University of Louvain}}{}{Belgium}{\textnormal{Co-author of 10 research papers.  Involvement in international projects and consortium (\href{http://www.jecam.org/}{JECAM}, \href{http://www.d4d.orange.com/en/Accueil}{D4D}, \href{https://www.earthobservations.org/geoglam.php}{GEOGLAM}, \href{http://www.geoglam-sigma.info/Pages/default.aspx}{SIGMA}...). Setting up successful research proposals (\href{http://maps.elie.ucl.ac.be/belcam/}{BELCAM}, \href{http://www.esa-sen2agri.org/SitePages/Home.aspx}{Sen2Agri}). Communications at international conferences and workshops (\href{https://sites.google.com/view/systemsanalysis/home}{CIMMYT}, \href{http://netmob.org/}{NetMob}, \href{http://fallmeeting.agu.org/2015/}{AGU}, \href{http://www.cesbio.ups-tlse.fr/multitemp/?p=2559}{CNES}, \href{https://colloque6.inra.fr/gv2m}{GV2M}...). Master thesis supervision and team work through collaborative research projects.}}

\cventry{2012}{Research Assistant}{\textsc{catholic University of Louvain}}{}{Belgium}{\textnormal{Geospatial product development from Satellite imagery for the monitoring of European biodiversity (\href{http://www.lifewatch.be/}{European Lifewatch project}). Identification of the best approach for monitoring and aggregating indicators of ecosystem dynamics.}}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Research Publications}

\cventry{2020}{Mobile Phone Data for Urban Climate Change Adaptation: Reviewing Applications, Opportunities and Key Challenges}{\textsc{Sustainability}}{}{Co-authors: Dujardin, S., Steele, J., and Linard, C.}{}

\cventry{2019}{Accuracy requirements for early warning of crop production in Senegal}{\textsc{arXiv}}{}{Co-authors: Defourny, P}{}

\cventry{2018}{Mobile Phone Metadata for Development}{\textsc{arXiv}}{}{}{}

\cventry{}{A Comparison of Global Agricultural Monitoring Systems and Current Information Gaps. Agricultural Systems.}{\textsc{Agricultural systems}}{}{Co-authors: Fritz, S., See, L,  Laso Bayas, J.C., Waldner, F.,  Becker-Reshef, I., Whitcraft, A., Baruth, B., Bonifacio, R.,  et al}{}

\cventry{}{Identifying seasonal mobility profiles from anonymized and aggregated mobile phone data. Application in food security}{\textsc{Plos One}}{}{Co-authors: Zufiria, P. J., Pastor-Escuredo, D., Ubeda-Medina, L. A., Hernandez-Medina, M. A., Barriales-Valbuena, I., Morales, A. J., Nkwambi, W., Diop, M. B.,  Quinn, J., Hidalgo-Sanchis, P., and Luengo-Oroz, M}{}

\cventry{}{Social capital and transaction costs in millet markets}{\textsc{Heliyon}}{}{Co-authors: Marinho, E., d’Andrimont, R., Waldner, F., Radoux, J., Gaspart, F., and Defourny, P}{}

\cventry{2017}{Combining disparate data sources for improved poverty prediction and mapping}{\textsc{Proceedings of the National Academy of Sciences}}{}{Co-authors: Marinho, E., d’Andrimont, R., Waldner, F., Radoux, J., Gaspart, F., and Defourny, P}{}

\cventry{}{A multi-disciplinary perspective on emergent and future innovations in peer review}{\textsc{F1000Research}}{}{Co-authors: Tennant, J. P., Dugan, J. M., Graziotin, D., Waldner, F., Mietchen, D., Elkhatib, Y., Collister, L. B., Pikas, C. K., Crick, T., et al}{}

\cventry{}{Sentinel-2’s Potential for Sub-Pixel Landscape Feature Detection}{\textsc{Remote Sensing}}{}{Co-authors: Radoux, J., Chomé, G.,  Waldner, F., Bellemans, N., Matton, N., Lamarche, C., d’Andrimont, R., and Defourny, P}{}

\cventry{2016}{The impact of training class proportions on binary cropland classification}{\textsc{Remote Sensing Letters}}{}{Co-authors: Löw, F., and Waldner, F}{}

\cventry{}{The academic, economic and societal impacts of
Open Access: an evidence-based review}{\textsc{F1000Research}}{}{Co-authors: Tennant, J. P., Waldner, F., Masuzzo, P., Collister, L. B., and Hartgerink, C. H}{}

\cventry{}{A Layered Vegetation Model for GPR Full-Wave Inversion}{\textsc{IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing}}{}{Co-authors:  Ardekani, M. R. M., and Lambot, S}{}

\cventry{2015}{A dynamic vegetation senescence indicator for near-real-time desert locust habitat monitoring with MODIS}{\textsc{Remote Sensing}}{}{Co-authors: Renier, C., Waldner, F., Babah Ebbe, M. A., Cressman, K., and Defourny, P}{}

\cventry{}{Genesis of millet prices in Senegal: The role of production, markets and their failures}{\textsc{NetMob}}{}{Co-authors: Marinho, E., d’Andrimont, R., Waldner, F. and Radoux, J}{}

\cventry{2014}{Monitoring dry vegetation masses in semi-arid areas with MODIS SWIR  bands}{\textsc{Remote Sensing of Environment}}{}{Co-authors: Kergoat, L., Hiernaux, P., Mougin, E., and Defourny, P}{}

\cventry{}{GPR data inversion for vegetation layer}{\textsc{15th International Conference on Ground Penetrating Radar}}{}{Co-authors: Ardekani, M. R., Neyt, X., Nottebaere, M., and Lambot, S}{}

%----------------------------------------------------------------------------------------
%	Conferences and workshops
%----------------------------------------------------------------------------------------
\section{Conferences and workshops}

\cventry{2019}{Guest Lecture}{\textsc{Dragon Training School}}{BioSense Insitute}{Serbia}{Title: Data Innovation for food security: Beyond research and development.}

\cventry{}{Panelist}{\textsc{Data Science Ghent}}{De Krook}{Belgium}{Theme: Data ownership}

\cventry{}{Organizers}{\textsc{Poverty Mapping Initiative}}{ITU AI for Good Global Summit}{Switzerland}{Dalberg Data Insights, the Qatar Computing Research Institute and the World Bank Group convened experts to share knowledge and make plans to better combine traditional development data with complementary sources of big data towards achieving more accurate, timely and cost-effective measures of poverty.}

\cventry{}{Guest Talk}{\textsc{Sceptics in the Pub}}{}{Belgium}{Title: Introduction to Open Access.}

\cventry{}{Talk}{\textsc{Ph.D. public defense}}{catholic University of Louvain}{Belgium}{Title: Harnessing the Data Revolution for food security and poverty mapping: synergies between mobile phone data, Earth Observation and official statistics in Senegal.}

\cventry{2017}{Talk}{\textsc{6th EUGEO Congress on the Geography of Europe}}{Académie royale des Sciences, des Lettres et des Beaux-Arts de Belgique}{Belgium}{Title: Dynamic population mapping in Belgium using mobile phone data.}

\cventry{}{Talk}{\textsc{CIMMYT Systems Analysis Workshop}}{catholic University of Louvain}{Belgium}{Title: Mobile Phone Metadata. Applications.}

\cventry{2016}{Organizers}{\textsc{Pechakucha Night}}{Val Benoit}{Belgium}{Theme: Open Science (12 speakers, $\sim$150 p.).}

\cventry{}{Organizers}{\textsc{Pechakucha Night}}{La Caserne Fonck}{Belgium}{Theme: Invisible Design (12 speakers, $\sim$200 p.).}

\cventry{}{Organizers}{\textsc{Pechakucha Night}}{La Cité Miroir}{Belgium}{Theme: Knowledge Mutation (12 speakers, $\sim$300 p.).}

\cventry{2015}{Poster}{\textsc{AGU Fall Meeting}}{Moscone}{USA}{Title: Crop monitoring as a tool for modelling the genesis of millet prices in Senegal.}

\cventry{}{Talk}{\textsc{Netmob}}{MIT}{USA}{Title: Genesis of millet prices in Senegal: the role of production, markets and their failures.}

\cventry{2014}{Poster}{\textsc{Global Vegetation Monitoring and Modeling International Conference}}{}{France}{Title:  Advanced sampling of remote sensing images for area estimation.}

\cventry{2013}{Talk}{\textsc{SPOT4 (Take5) Users Day}}{CNES}{France}{Title: Preparing for the exploitation of Sentinel-2 observations for agriculture monitoring.}

\cventry{2012}{Poster}{\textsc{4th AMMA International Conference}}{Meteo France}{France}{Title: Monitoring straw and litter masses with MODIS during the
dry season in Sahel.}

%----------------------------------------------------------------------------------------
%	Coursework SECTION
%----------------------------------------------------------------------------------------

\section{Awards and grants}

\cventry{2018}{4th place in the Hackathon Hacking for Impact}{\textsc{McKinsey}}{}{}{Machine learning hackathon on predicting the probability of patient survival based on given variables.}
\cventry{}{Most Inspiring Project Prize Winner}{\textsc{NASA Space Apps Challenge (Liège edition)}}{}{}{Prototyping a game application for crowdsourcing validation data for land cover maps.}
\cventry{2015}{\$2k Agriculture Prize}{\textsc{Data For Development Challenge (D4D)}}{}{}{Social challenge on Big Data in Senegal organized by Orange in collaboration with UN and MIT.}
\cventry{}{\$45k Research Grant}{\textsc{Bill \& Melinda Gates Foundation}}{}{}{A selection of winning D4D teams (6 out of hundred) received a grant to scale up their solution in Senegal.}
\cventry{2012}{4-year Ph.D Grant}{\textsc{F.R.S.-FNRS FRIA}}{}{}{Doctoral scholarship awarded on the basis of a selection process (success rate 25\%).}




%----------------------------------------------------------------------------------------
%	Coursework and trainings work
%----------------------------------------------------------------------------------------
\section{Coursework and trainings}

\cventry{2018}{International School of Physics "Enrico Fermi"}{\textsc{Italian Physical Society}}{Computational Social Science and Complex Systems}{}{This school is one of the most significant cultural activities of the Italian Physical Society and has reached considerable international prestige.}
\cventry{2014}{BSE Academy}{\textsc{Impulse Brussels}}{}{}{Entrepreneurial training program of 3 months.}

%----------------------------------------------------------------------------------------
%	ENtrepneurship SECTION
%----------------------------------------------------------------------------------------
\section{Entrepreneurship experience}

\cventry{2015}{\href{https://youtu.be/LXkT-cnFTLs}{Food Porn Show}}{\textsc{Gastronomical Recipe Kits}}{}{Belgium}{Co-founder of an "all-in-one" gastronomical recipe kits delivery service for fine dining recipes. Building the company from 0 to 1: market research, financial analysis, product development, marketing strategy, pre-launch. The project was stopped after the Beta phase.  }
\cventry{2014}{Stemgarden}{\textsc{Bring Nature back to the City}}{}{Belgium}{Selected project for BSE Academy : entrepreneurial training program of 3 months by Impulse Brussels. The initial project was an \href{https://vimeo.com/88909073}{indoor gardening system in bamboo} that has evolved into a \href{https://stemgarden.co/}{web platform} for sharing innovative gardening ideas.}

%----------------------------------------------------------------------------------------
%	Volunteer work
%----------------------------------------------------------------------------------------
\section{Volunteer work}

\cventry{2015 - 2019}{\href{https://web.archive.org/web/20190822234152/http://www.guru-gis.net/}{Co-founder of Guru-Gis.net}}{\textsc{Coding Blog}}{}{}{Blog on geospatial and remote sensing analysis using R, Qgis and OTB.}
\cventry{2015 - 2017}{Organizers of Pechakucha Night}{\textsc{Gotoro}}{}{}{Promote entrepreneurial spirit through the organization of \href{http://pechakuchaliege.be/}{PechaKucha Night conferences in Liège} ($\sim$200p.).}
\cventry{2014 - 2017}{Member of Focus Research}{\textsc{Belgian Research Policy Group}}{}{}{Belgian research lobby. Publication of \href{https://www.dropbox.com/s/idtqteiizjmqqbd/magazine_2015_objectif_recherche.pdf?dl=0}{the Research in Transition} (20 000 copies) distributed in all the french-speaking universities in Belgium.}
\cventry{2014 - 2016}{Co-founder of PhD Hub}{\textsc{Belgian Network for Early Career researchers}}{}{}{Networking organisation aiming to connect young Belgian researchers to each other. Organization of Social events for Early Career researchers such as PhD parties (100 - 250 p.). }
\cventry{2014 - 2015}{Belgian delegate of Eurodoc}{\textsc{\href{http://www.eurodoc.net}{European Council of Doctoral Candidates and Junior Researchers}}}{}{}{Federation of 32 national organisations of PhD candidates with the aim of bringing the voice of young researchers to the attention of European policy-makers. Promotion of Open Access in the dedicated Working Group (webinar organization, \href{http://f1000research.com/articles/5-632/v1}{paper writing}).}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
\cvitem{Background}{I provide both technical and strategic consulting in data innovation. I have a mixed profile combining the mindset of an \textbf{engineer}, the passion of a \textbf{researcher}, the skills of a \textbf{data scientist}, the drive of an \textbf{entrepreneur} and the agility of a \textbf{consultant}. }{}
\cvitem{How I work}{For ideation sessions and strategy consulting, I like to tap into the \textbf{design-thinking} toolbox to maximize the output of a workshop. I prefer to work in close collaboration with the client if possible \textbf{physically} or \textbf{remotely} with frequent interactions. I do my statistical analysis and data analysis mainly in \textbf{R} (even if I sometimes use \textbf{Python} if necessary). I favour working with a \textbf{causal inference} approach rather than pure prediction. That being said, I can run a \textbf{machine learning} algorithm if it seems to be the right solution. I like to build \textbf{dockerized interactive web applications} to communicate results and support decision making. I realize the backend in \textbf{Shiny} with the use of cloud computing for database management (example \textbf{Big Query}). For the front end, I use a classic combination of \textbf{HTML}, \textbf{javascript} and \textbf{CSS}. I share research code and tools on \textbf{Github}. I write papers using \LaTeX. I work best on a \textbf{Unix-based} machine.}{}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitem{Fluent}{\textbf{French, English}}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}



